\documentclass[./main.tex]{subfiles}
\begin{document}

\chapter{CONCLUSION AND FUTURE WORK}
\section{Conclusion}
\noindent
In conclusion, the development of a stock price prediction system utilizing a machine learning model, specifically LSTM, holds great promise in enhancing the financial decision-making process. With the expected outcome of this system, investors and analysts will have a robust tool at their disposal, offering accurate stock predictions and risk management capabilities. The extensive research and incorporation of the latest industry trends underscore the commitment to providing users with valuable insights into the stock market's complexities. By empowering users to make informed investment decisions, this system aims to not only improve profitability but also mitigate financial risks. In an ever-evolving financial landscape, such a system can be a valuable asset for those seeking to navigate the stock market with greater confidence and effectiveness.
\section{Future Work}
\noindent
The future work for this project includes the following:
\begin{itemize}
    \item \textbf{Enhanced Model Performance:} The LSTM model's performance can be further enhanced by incorporating additional features and data sources. This can include the integration of social media sentiment analysis, news articles, and other relevant data to improve the model's predictive capabilities.
    \item \textbf{Real-time Data Integration:} The system can be further developed to incorporate real-time data feeds, enabling users to access the latest market information and predictions. This can provide users with up-to-the-minute insights and enhance the system's overall utility.
    \item \textbf{Scalability and Performance Optimization:} As the user base and data volume grow, the system's scalability and performance optimization become critical. Future work can focus on enhancing the system's scalability and optimizing its performance to accommodate increasing demands.
\end{itemize}
\end{document}