\documentclass[./main.tex]{subfiles}
\begin{document}

\chapter{ BACKGROUND STUDY AND LITERATURE REVIEW }

% Specify the numeric citation style
\label{chap:background}
\section{Background Study}
Stock price prediction has been a longstanding challenge in financial markets. Accurate predictions are essential for investors, traders, and financial institutions to make informed decisions. Machine learning has gained significant attention in recent years as a promising approach for improving the accuracy of stock price predictions.\cite{CHEN2023106038}.
\noindent
 % \subsection {Early Attempts at Predicting Stock Prices} 
 In the early days of trying to predict stock prices, people mainly used traditional math and statistics. They looked at stock charts, used a method called time series analysis, and some math tools like moving averages. Then, in the 1960s and 70s, a person named Benoit Mandelbrot came up with the idea of using something called "fractal analysis" to understand how stock prices move. But it's important to know that these early methods had problems because they couldn't really figure out the complicated and always-changing nature of the stock market.\cite{mandelbrot1963variation}
 \noindent
  % \subsection {Machine Learning In Stock Forecasting} 
  Machine learning algorithms have brought a fresh perspective to research on predicting stock prices. Studies have demonstrated several methods for forecasting stock prices as a result Some of them are below.
 
  \noindent
    \textbf{Neural Networks}:Neural networks have gained popularity in recent years for various machine learning tasks, including stock price prediction \cite{ZHANG2021872}. Some neural network algorithms, such as Recurrent Neural Networks (RNNs) and Artificial Neural Networks (ANNs), are commonly practiced for predicting stock prices.
     
     
       \noindent
     \textbf{Random Forest Algorithm}: Random Forest is a machine learning algorithm introduced by Leo Breiman in 2001 \cite{breiman2001random}. It is an ensemble learning method that combines the predictions of multiple decision trees to improve accuracy and reduce overfitting.
   

\noindent 
    \textbf{SVM}:In the initial phases of applying machine learning to predict stock prices, the Support Vector Machine (SVM) was utilized. It employed the Support Vector Regression algorithm \cite{BENIWAL2023110566}
      


\newpage
        
\section{Literature Review}
Literature survey is the process in which a complete and comprehensive review is
conducted encompassing both the published and unpublished work from other
alternative sources of information. This review is conducted in the domains of
specific interest to the person or researcher. Further, the results of this process are
documented.
\medskip
\newline
\noindent
"Accurately predicting the change of stock price can reduce the investment risk of stock investors and effectively improve the investment return". \cite{lu2021cnn-bilstm-am}
Because of the stock market's inherent volatility, predicting stock prices typically involves complex nonlinear time series forecasting. Stock prices are influenced by a multitude of variables, making accurate prediction challenging with simplistic models.
\medskip
\newline
\noindent 
Another Survey on \textit{"Chaos theory"}, a branch of mathematics and physics, has found intriguing applications in the field of finance,
offering a fresh perspective on understanding and predicting market dynamics. This theory posits that complex systems, such as financial markets, are inherently sensitive to initial conditions and can exhibit chaotic, unpredictable behavior, even though they may appear random at first glance. \cite{KLIOUTCHNIKOV2017368} 
One of the fundamental concepts of chaos theory is the "butterfly effect." It suggests that a small event, like the flapping of a butterfly's wings, can trigger a cascade of effects that ultimately lead to major, seemingly unrelated events. In the context of finance, this means that minor changes or perturbations in market conditions can have far-reaching consequences. 
Chaos theory's recognition of unpredictability and sudden shifts in financial markets underscores the importance of robust risk management strategies. By acknowledging the potential for chaotic behavior, 
investors and institutions can better prepare for unforeseen market events.
\medskip
\newline
\noindent
The stock market is significantly impacted by the behavior and trends on social media. 
Conducting sentiment analysis on social media content can provide valuable insights into trader sentiment and market trends. This, in turn, aids in risk management by allowing for proactive analysis of real-time news and market behavior. \cite{bollen2011twitter} 
\medskip
\newline
\noindent 
Selecting a model for stock price prediction has become more accessible, despite the dynamic behavior of the stock market. Recurrent Neural Networks (RNN) excel in this context, primarily due to their ability to retain and utilize prior states in current state calculations. Unlike independent layers, the hidden layers in RNN are interconnected, incorporating not just input layer outputs but also outputs from preceding hidden layers. This characteristic empowers RNN to perform well with sequential data. RNN's advantage lies in its capacity to consider the contextual information within the data during training, making it particularly suitable for stock and Forex scenarios. This is because fluctuations at a specific time often bear a connection to the previous trends. \cite{asi4010009}
\medskip
\newline
\noindent
"Long Short-Term Memory (LSTM) networks have brought a revolutionary shift in the landscape of stock analysis". \cite{ZHANG2021872} 
\noindent
 LSTM networks stand out as the best choice in stock analysis due to their versatility in capturing complex temporal patterns, handling non-linearity, and automatically learning significant features within financial time series data. They empower traders and analysts with an advanced tool for understanding market dynamics and making informed decisions. As research in this field continues to grow, the significance of LSTMs in stock analysis becomes increasingly evident, and their influence in the financial world is set to expand, providing traders with a powerful ally in navigating the intricacies of the stock market. \cite{zhang2018stock}
\noindent
\section*{Study of existing system}
On our research we have found various related application on stock price prediction and stock analysis
\newline
\noindent
\textbf{Chukul NEPSE}
 is an  AI-based algorithm Application that aims to predict the trend of Nepal stock market. 
 It is a tool that facilities a trader to make decisions without having to do any technical and fundamental research. 
 They also provide a platform for the user to learn about the stock market and its various aspects.
 Chukul provides a novice user a safe landing in this unpredictable environment of rumor filled share market. It saves a lot of analysis time regarding the rise and fall of the share value\cite{chukul-nepse}. 
\newline 
\noindent
\textbf{Nepal Stock Exchange}
is a mobile Application and web based application that provides updates of daily ups and down in NEPSE.
The app provides real-time access to market data, news, and insights pertinent to the Nepal Stock Exchange. 
The app also provide Comprehensive Analysis of NEPSE Data and news related to Nepal Share Market.
Not only that, the app also provides the latest news and updates related to the share market of Nepal. 
\cite{Nepal-share}
\newline
\noindent
 \textbf{Saral Lagani} is a web based application developed for NEPSE Stock analysis and news publication. 
The app provides real-time access to market data, news, and insights pertinent to the Nepal Stock Exchange.
This system have tools to analyze stock with interactive graphs and stastical measurements \cite{Saral-Lagani}
 \newline 
 \textbf{Yahoo-finance}
is a web based application that provides stock market data and news. The service covers over 350 exchanges in over 80 countries.
Yahoo Finance provides access to more than 5 years of daily OHLC price data. The data can be downloaded in CSV format or accessed through an API.
Yahoo Finance also provides access to company news and financials through its website and mobile app. \cite{yahoo-finance}

\end{document}